---
output:
    html_document:
      toc: true
      toc_float: true
      highlight: null
      theme: default
---
<html lang="en">
<header>
  <meta charset="utf-8"/>
  <title>Include a Subtitle and TOC</title>
  <h1 class="title toc-ignore">Include a Subtitle and TOC</h1>
  <h2 class="subtitle toc-ignore">Some Sensible Subtitle</h2>
  <h3 class="author toc-ignore">leyshr</h3>
  <h3 class="date toc-ignore">03 Dec 2021</h3>
</header>
<body>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = "")
```
  
## Adapted R Markdown

This R Markdown template has been adapted using the 'accessrmd' package. This
template has a different header and HTML structure to the standard R markdown
template. This is to improve the accessibility of the knitted HTML documents for
screen readers.

For more help in using R Markdown see <http://rmarkdown.rstudio.com>.

Clicking the **Knit** button will generate a document including typed content
and the output of any R code chunks. For example:
    
```{r cars}
summary(cars)
```

## Plots
  
```{r pressure, echo=FALSE, message=FALSE}
plt <- ggplot2::ggplot(
  pressure,
  ggplot2::aes(temperature, pressure)
  ) +
  ggplot2::geom_point()

accessrmd::access_img(
  plt, 
  alt = "Vapor Pressure of Mercury as a Function of Temperature",
  ht = 400
  )

```

In the above chunk, `echo=FALSE` was used to hide the R code that produced the
plot from the knitted HTML document. `message=FALSE` was also used to stop
  messages being knitted to the HTML output.</body>
</html>
