
<html lang="en">
<header>
  <meta charset="utf-8"/>
  <title>You Need To Provide A Title.</title>
  <h1 class="title toc-ignore">You Need To Provide A Title.</h1>
  <h2 class="author toc-ignore">richardleyshon</h2>
  <h2 class="date toc-ignore">02 Nov 2021</h2>
</header>
<body>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
  
## Adapted R Markdown

This R Markdown templated has been adapted using the 'accessrmd' package. This
template has a different head and HTML structure to the standard R markdown
template. This is to improve the accessibility of the knitted HTML documents for
screen readers.

For more help in using R Markdown see <http://rmarkdown.rstudio.com>.

Clicking the **Knit** button will generate a document including typed content
and the output of any R code chunks. For example:
    
```{r cars}
summary(cars)
```

## Plots
  
```{r pressure, echo=FALSE}
plot(pressure)
```

In the above chunk, `echo = FALSE` was used to hide the R code that produced the
plot from the knitted HTML document.</body>
</html>
