---
output:
    html_document:
      toc: true
      toc_float: true
---
<html lang="en">
  <header>
    <meta charset="utf-8"/>
    <title class="toc-ignore">testing hybrid html</title>
    <h1 id="title toc-ignore" class="toc-ignore">testing hybrid html</h1>
    <h2 class="header_h2s toc-ignore">richardleyshon</h2>
    <h2 class="header_h2s toc-ignore">06 Oct 2021</h2>
  </header>
  <body>






```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
  
## Adapted R Markdown

This R Markdown templated has been adapted using the 'accessrmd' package. This
template has a different head and HTMl structure to the standard R markdown
template. This is to improve the accessibility of the knitted HTML documents for
screen readers.

For more help in using R Markdown see <http://rmarkdown.rstudio.com>.

Clicking the **Knit** button will generate a document including typed content
and the output of any R code chunks. For example:
    
```{r cars}
summary(cars)
```

## Plots
  
```{r pressure, echo=FALSE}
plot(pressure)
```

In the above chunk, `echo = FALSE` was used to hide the R code that produced the
plot from the knitted HTML document.</body>
</html>
